\LARGE \bf Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting

### 2014-12-11 main.tex
Change 'has been's to 'is'

Teachable computer-based agents have previously been used to encourage the 
``protégé effect'', wherein students invest more effort into learning when it
is for a teachable agent than for themselves~\cite{Chase2009}. As we are 
concerned with learning of a physical skill, the learning agent developed has 
been embodied in a humanoid robot which is capable of physically demonstrating 
handwriting trajectories to its child learning partner.
This is supported by the potential for motor mimicry to yield significant 
improvements in handwriting interventions in which letter formations are 
demonstrated to participants~\cite{Berninger1997}.

@@

For the development of a learning algorithm in the context of
handwriting, a parameterisation of letters and their deformities has been sought such 
that different quality shapes can be generated, depending on the parameters input to
the letter models. This allows us to configure the system such as to improve its writing 
by modifying the parameters based on feedback from the 
reinforcement learning partner (Section~\ref{sec:learningAlg}).

@@

PCA has been performed on a set of letter paths captured from a digital pen,
using the UJI Pen Characters 2 dataset \cite{Llorens2008} with 120 instances of
each letter (2 repetitions from 60 adult users). While it may be appropriate in future work to
identify the location of salient features of the shapes which are robust to 
unanticipated user input (such as shapes drawn backwards),
the features are currently taken as $n$ uniformly spaced points along the shape
path. The
points are arranged into an observation vector presented in (\ref{eq:obsVec}),
where $x_i$ and $y_i$ represent the coordinates of each of the points along the
path. The observation shapes are normalised to have a unit maximum dimension 
and centre at the origin.

@@

PCA has been performed on all of the paths of a particular allograph in the
dataset individually, to reduce the $2n$-dimensional space for that shape to one 
with $N=10$ dimensions.
As such,
each shape may be approximated by the mean shape of the allograph plus a sum of the top 10
eigenvectors, weighted by the parameter vector ${\bf p}$. 
%Indeed, the amount of variance in the dataset
%that is explained by each eigenvector ${\bf v}_i$ is $\sqrt{\lambda_i}$, and
%therefore the proportion of the variance explained by each dimension/eigenvector
%is as shown in (\ref{eq:proportionVar}).
%
%\begin{equation}\label{eq:proportionVar}
%\%var_i = \frac{\sqrt{\lambda_i}}{\sum_{i=1}^{N}\sqrt{\lambda_i}}\times 100\%
%\end{equation}

@@

For the statistical shape model employed by the system, the method for
responding to user demonstrations is to move the learning algorithm's parameters
towards those of the demonstration. In the results presented in this work, the
linear update equation shown in (\ref{eq:update}) has been used, where ${\bf p}$ is the
learned parameter vector at time step $k$, and $\alpha$ is the learning rate,
between 0 and 1.

@@

The {\sc nao} V4 humanoid robot, which has been developed by Aldebaran Robotics and 
purposely designed to look approachable \cite{Gouaillier2008}, has been used for
this work. It is a commercially affordable biped robot, 58cm tall, with 25
degrees of freedom, two cameras, speech capabilities and the ability to
autonomously execute a range of tasks.

@@

Using simulated handwriting provides an opportunity for the robot's writing to
appear smoother than would be achievable with a writing instrument. However, the
robot's motions must still sufficiently match the displayed trajectory in order
capture the engagement of the child participant in the action. Aldebaran's NaoQi API
has been used for the inverse kinematics of the trajectory following. The Robot
Operating System (ROS)\footnote{The ROS stack for {\sc nao} is available at:
\url{http://wiki.ros.org/nao_robot}.} has been used for integration of the {\sc nao}
with external reference frames, such as the tablet's location, 
using the $tf$ transformation library \cite{Foote2013}.

@@

An Android application has been developed to receive the trajectory message over
a ROS topic and display the trajectory as an
animation. Synchronisation between the tablet and the robot has been achieved by
using NTP servers to synchronise device clocks; passing only the necessary number of points (7)
to the robot's motion planner to improve timing accuracy; and not running 
computationally expensive tasks on the robot (such as camera publishing) while it 
is writing.

@@

    \item developing capabilities for a robot with limited fine motor
        capabilities, in particular the {\sc nao} robot, to engage in the act of handwriting in a
        way which is believable for interacting with children. This has been
        accomplished by leveraging simulated handwriting with a synchronised
        tablet communicating via ROS;

>>>>

Teachable computer-based agents have previously been used to encourage the 
``protégé effect'', wherein students invest more effort into learning when it
is for a teachable agent than for themselves~\cite{Chase2009}. As we are 
concerned with learning of a physical skill, the learning agent developed is 
embodied in a humanoid robot which is capable of physically demonstrating 
handwriting trajectories to its child learning partner.
This is supported by the potential for motor mimicry to yield significant 
improvements in handwriting interventions in which letter formations are 
demonstrated to participants~\cite{Berninger1997}.

@@

A parameterisation of letters and their deformities was sought such 
that different quality shapes can be generated, depending on the parameters input to
the letter models. This allows us to configure the system such as to improve its writing 
by modifying the parameters based on feedback from the 
reinforcement learning partner (Section~\ref{sec:learningAlg}).

@@

PCA is performed on a set of letter paths captured from a digital pen,
using the UJI Pen Characters 2 dataset \cite{Llorens2008} with 120 instances of
each letter (2 repetitions from 60 adult users). While it may be appropriate in future work to
identify the location of salient features of the shapes which are robust to 
unanticipated user input (such as shapes drawn backwards),
the features are currently taken as $n$ uniformly spaced points along the shape
path. The
points are arranged into an observation vector presented in (\ref{eq:obsVec}),
where $x_i$ and $y_i$ represent the coordinates of each of the points along the
path. The observation shapes are normalised to have a unit maximum dimension 
and centre at the origin.

@@

PCA is performed on all of the paths of a particular allograph in the
dataset individually, to reduce the $2n$-dimensional space for that shape to one 
with $N=10$ dimensions.
As such,
each shape may be approximated by the mean shape of the allograph plus a sum of the top 10
eigenvectors, weighted by the parameter vector ${\bf p}$. 
%Indeed, the amount of variance in the dataset
%that is explained by each eigenvector ${\bf v}_i$ is $\sqrt{\lambda_i}$, and
%therefore the proportion of the variance explained by each dimension/eigenvector
%is as shown in (\ref{eq:proportionVar}).
%
%\begin{equation}\label{eq:proportionVar}
%\%var_i = \frac{\sqrt{\lambda_i}}{\sum_{i=1}^{N}\sqrt{\lambda_i}}\times 100\%
%\end{equation}

@@

For the statistical shape model employed by the system, the method for
responding to user demonstrations is to move the learning algorithm's parameters
towards those of the demonstration. In the results presented in this work, the
linear update equation shown in (\ref{eq:update}) is used, where ${\bf p}$ is the
learned parameter vector at time step $k$, and $\alpha$ is the learning rate,
between 0 and 1.

@@

The {\sc nao} V4 humanoid robot, which has been developed by Aldebaran Robotics and 
purposely designed to look approachable \cite{Gouaillier2008}, is used for
this work. It is a commercially affordable biped robot, 58cm tall, with 25
degrees of freedom, two cameras, speech capabilities and the ability to
autonomously execute a range of tasks.

@@

Using simulated handwriting provides an opportunity for the robot's writing to
appear smoother than would be achievable with a writing instrument. However, the
robot's motions must still sufficiently match the displayed trajectory in order
capture the engagement of the child participant in the action. Aldebaran's NaoQi API
is used for the inverse kinematics of the trajectory following. The Robot
Operating System (ROS)\footnote{The ROS stack for {\sc nao} is available at:
\url{http://wiki.ros.org/nao_robot}.} is used for integration of the {\sc nao}
with external reference frames, such as the tablet's location, 
using the $tf$ transformation library \cite{Foote2013}.

@@

An Android application has been developed to receive the trajectory message over
a ROS topic and display the trajectory as an
animation. Synchronisation between the tablet and the robot is achieved by
using NTP servers to synchronise device clocks; passing only the necessary number of points (7)
to the robot's motion planner to improve timing accuracy; and not running 
computationally expensive tasks on the robot (such as camera publishing) while it 
is writing.

@@

    \item developing capabilities for a robot with limited fine motor
        capabilities, in particular the {\sc nao} robot, to engage in the act of handwriting in a
        way which is believable for interacting with children. This is
        accomplished by leveraging simulated handwriting with a synchronised
        tablet communicating via ROS;
